### 2013-03-04 eusflat2013/proposal.tex
new version for the eusflat2013

\subsection{\label{subsec:eval-allen-relations}Evaluation of the Allen's Relations}

In this section we will analyze first the calculation of all the possible Allen's relations between a crisp time point and an ill-known time point and between a crisp time point and an uncertain time indication (UTI). Then, we will compare two ill-known time points and two uncertain time indications.

>>>>

\subsection{\label{subsec:eval-allen-relations}Evaluation of the Allen's Relations}
As it has been shown in Table \ref{tab:urz}, when using UTIs in the triangular model, it is possible to obtain a more detailed relational information (there are fifteen possible relations) than with the ill-known constraint approach. The following observations should be taken into account when extracting relational information from both frameworks:

\begin{itemize}
 \item In TM, the Allen's Relations $R \in \left \lbrace B, O, C, D, OB, A \right \rbrace$ between an interval point $J$  and an UTI $\pi_I$ are computed by Eq. \eqref{eq:possibility-iz-uti-certain}. Therefore, for the Allen's Relations in $R$, 
 possibility that an Allen Relation between an interval point $J$  and an UTI $\pi_I$ is $1$ if the interval point $J$ is in the Allen Relation, or $0$ in other case.
\item In the TM, the other nine Allen's Relations between an interval point $J$ and an UTI $\pi_I$ are graded from $1$ to $0$ and computed by using the Eq. \eqref{eq:possibility-iz-uti}. 
\item In the ill-known constraint framework, all the thirteen Allen's Relations are computed by using an aggregation of ill-known constraints (see Table \ref{tab:allen-relations}). Therefore, the possibility that a time point $J$ is in a given Allen Relation is always graded from $1$ to $0$.
\end{itemize}

For example, consider that we want to know whether the relation Before (B) holds between a time point $J$ and an IKTI $I$. We will note $\Pos \left(C_B (J)  \right)$ the possibility that the relation before holds. There are three possibilities:
\begin{enumerate}
 \item $\Pos \left(C_B (J)  \right)$ = 1: The time point $J$ is before the IKTI $I$.
\item $\Pos \left(C_B (J)  \right)$ = 0: The time point $J$ is not before the IKTI $I$.
\item $0 < \Pos \left(C_B (J)  \right) < 1$: The time point $J$ is to some extent before the IKTI $I$.
\end{enumerate}

The last case corresponds in the TM to case when the before relation is one of the possible relations (See Table \ref{tab:urz}). That is, one of $\left \lbrace PM, PMB, UB \right \rbrace$.

The following table establishes the correspondences between the Allen's relations in the TM and in the ill-known constraints framework.

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
Symbol & Name & Possible Relations \\
\hline
B & Before & B, PM, PMB, UB \\
\multirow{2}{*}
{O} & Overlaps & O, PM, PS, PFB,\\
     &          &  PE, PMB, UB \\
C & Contains & C, PFB, PE, PSB \\
\multirow{2}{*}
D & During & D, PS, PE, \\
  &         &  PMB, UB  \\
OB & Overlapped by & OB, PE, PSB, PF \\
A & After & A, PF, UE \\
M & Meets & M, PM, PMB, UB \\
MB & Met By & MB, PF, UE \\
E & Equals & E, PE \\
\multirow{2}{*}
S & Starts & S, PS, PE, \\
  &         &   PMB, UB \\
SB & Started by & SB, PE, PSB \\
F & Finishes & F, PE \\
FB & Finished By & FB, PE, PFB\\
\hline
\end{tabular}
\caption{Correspondences between the Allen's Relations in the ill-known constraint framework and the triangular model,}
\label{tab:correspondences-tm-ikcf}
\end{table}

We will illustrate the calculation of one Allen Relation with an example.
\begin{example}
Consider a crisp time interval $J = [1, 3]$ the two ill-known time points $S, E$ that define a time interval. 
We want to obtain the possibility that $J$ is before the time interval.
The points are defined by two triangular membership functions $\mu_S$, $\mu_E$.

\begin{align}
\label{eq:ex-point}
\pi_S &= \mu_S = \left[2,5,7 \right] \\
\pi_E &= \mu_E = \left[9,12,15 \right]
\end{align}

Then, it is possible to define both an IKTI $I$ Eq. \eqref{eq:ex-uti-ikti} and an UTI $\pi_I$ Eq. \eqref{eq:ex-uti-uti}. The intervals are illustrated in Figure \ref{fig:example}.

\begin{figure}[h]
   \centering
   \includegraphics[scale=1.5]{graphs/example.eps}
   \caption{In the top, the crisp time interval $J$ and the IKTI given by $I = [S, E]$. The ill-known constraint for the before relation is illustrated in grey color. In the lower graphic, the interval point $J$ and the UTI $\pi_I$. }
   \label{fig:example}
 \end{figure}

\begin{align}
\label{eq:ex-uti-ikti}
I = \left[S, E \right]\\
\label{eq:ex-uti-uti}
\mu_I = \left(\mu_S, \mu_E \right)
\end{align}

First we will obtain the possibility between $J$ and the UTI $\pi_I$. The relation possibly meets has three candidates: Before, Meets and Overlaps.

\begin{align}
  \mu_{\left(J R \pi_I \right)}(B) &= \sup_{a < e} \pi_S(a)\\
\mu_{\left(J R \pi_I \right)}(M) &= \pi_S(e)\\
\mu_{\left(J R \pi_I \right)}(O) &= \sup_{a > e} \pi_S(a)
\end{align}

\begin{align}
\mu_{\left(J R \pi_I \right)}(B) &= 0.67\\
\mu_{\left(J R \pi_I \right)}(M) &= 0.33\\
\mu_{\left(J R \pi_I \right)}(O) &= 0
\end{align}

In order to compute the possibility  for the before relation between the crisp interval $J$ and the IKTI $I$, a ill-known constraint is needed.

\begin{equation}
 C_1\stackrel{\triangle}{=} \left(<,X\right)
\end{equation}

Then the possibility is computed as follows:

\begin{align}
\Pos \left(C_1 (J) \right) &= \sup_{a < e} \pi_S(a)\\
\Pos \left(C_1 (J) \right) &= 0.67 
\end{align}

\end{example}

% 
% In this section we will analyze first the calculation of all the possible Allen's relations between a crisp time point and an ill-known time point and between a crisp time point and an uncertain time indication (UTI). Then, we will compare two ill-known time points and two uncertain time indications.
